\section{Limitations}

The study is observational. Score state is endogenous to prior performance, and tactical behavior can precede and follow scoring. Opponent responses, substitutions, fatigue, and tactical adjustments occur simultaneously, so direction and mechanism are not identified. Unobserved within-match context can remain after adjustment, and team fixed effects remove only stable between-team differences.

The sample covers one international tournament with 32 national teams and 64 matches. National teams differ in preparation time, player pools, tactical systems, and schedule. Clustered uncertainty based on 64 matches may be sensitive to a small number of influential matches, and results may not generalize to domestic leagues, other tournaments, or later provider releases.

Pressure is provider-defined. The two-second sequence rule and five-second controlled-regain rule are analytical definitions, not universal tactical boundaries. Event-derived opponent passes, possessions, and possession time approximate opportunity rather than continuous control. Minimum denominator thresholds trade coverage for reliability, and conclusions can vary under alternative thresholds and exposures.

StatsBomb 360 contains event-linked visible freeze frames rather than continuous tracking. Coverage is incomplete overall and for Pressure events, and off-camera players cannot be inferred. The confirmatory models do not use 360 context; any spatial extension would require coverage analysis and visible-area adjustment.

The model diagnostics identify a one-column rank deficiency among nuisance indicators. A generalized inverse yields reproducible primary contrasts, but individual nuisance coefficients are not uniquely parameterized. Robustness-specific residual and influence diagnostics were not uniformly recomputed, limiting model-by-model diagnostic comparison. Missing values remain missing rather than zeros, but selective missingness may still affect eligible samples.

Finally, post-regain shots, xG, and xT use smaller effective samples and opportunity-normalized definitions. Goal conversion was unavailable in the analysis-ready table. Secondary and exploratory findings are not protected by the Holm procedure used for the two primary families. All conclusions are therefore restricted to adjusted observational associations in this dataset.
